---
output:
  html_document:
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
resource_files:
- hh_crosswalk.csv
- Rad_Onc_Data.csv
- Radiology_Data.csv
- Radiology_Site_Mapping.csv
- Epic Department Mapping Correction.csv
- hh_crosswalk.csv
- Radiology_Data.csv
- Rad_Onc_Data.csv
- Radiology_Site_Mapping.csv
- Epic Department Mapping Correction.csv
- open_encounters_exclusion.xlsx
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```
<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: auto;
  margin-right: auto;
}
</style>
<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>
<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>
<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>
```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 10000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  #library(zipcode)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(RODBC)
  library(DBI)
  library(odbc)
})
```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Import Data, echo = FALSE, warning = FALSE, message = FALSE}
'%!in%' <- function(x,y)!('%in%'(x,y))
inc_sites <- c("NETWORK","MSM","MSH-MSDFP","ONCOLOGY","MSW","MSBI","MSUS","MSH- AMBULATORY CARE","MSDD")


scheduling_data_raw <- as.data.frame(readRDS("/nfs/data/Applications/Ambulatory/Data_Updated/historical_data.rds")) %>%
  filter(!is.na(Campus)) %>%
  filter(Campus %in% c("NETWORK","MSM","MSH-MSDFP","ONCOLOGY","MSW","MSBI","MSUS","MSH- AMBULATORY CARE","MSDD")) 

# scheduling_data_raw <- as.data.frame(readRDS(file.choose())) %>%
#   filter(!is.na(Campus)) %>%
#   filter(Campus %in% c("NETWORK","MSM","MSH-MSDFP","ONCOLOGY","MSW","MSBI","MSUS","MSH- AMBULATORY CARE","MSDD"))

date_start <- as.Date("2021-01-01", format="%Y-%m-%d")
date_end <- as.Date(max(scheduling_data_raw$Appt.Made.DTTM), format="%Y-%m-%d")
# date_start <- as.Date(paste0(format(as.Date(date_end) - 365, "%Y-%m"),"-01"), format="%Y-%m-%d")

scheduling_data_raw <- scheduling_data_raw %>%
  mutate(Appt.WeekNum = lubridate::epiweek(Appt.DateYear),
         Visit.Method  = case_when(Visit.Method == "IN PERSON" ~ 'IN PERSON',TRUE ~ 'TELEHEALTH'),
         New.PT2 = case_when(New.PT2 == "New" ~ 'New', TRUE ~ 'Established'),
         New.PT3 = case_when(New.PT3 == "TRUE" ~ 'New',TRUE ~ 'Established'),
         enc.status = case_when(ENC_CLOSED_CHARGE_STATUS %in% c("OPEN", "CLOSED BUT COSIGN NEEDED") ~ 'OPEN',TRUE ~ 'CLOSED'),
         open.hours = ifelse(enc.status == "OPEN",
                             as.numeric(round(difftime(max(date_end)+1, Appt.DTTM, units = "hours"))),
                             as.numeric(round(difftime(Y_ENC_CLOSE_TIME, Appt.DTTM, units = "hours")))),
         open.days = round(open.hours/24)) %>%
   mutate(Appt.Made.DateYear = as.Date(Appt.Made.DTTM, format="%Y-%m-%d"),
          Appt.Made.MonthYear = format(as.Date(Appt.Made.DTTM, format="%m/%d/%Y"), "%Y-%m"),
          Appt.Made.Year = format(as.Date(Appt.Made.DTTM, format="%m/%d/%Y"), "%Y"),
          Appt.Made.WeekNum = as.numeric(strftime(Appt.Made.DTTM, format = "%V")))
```


```{r Data Processing, echo = FALSE, warning = FALSE, message = FALSE}

# Missing Charges (Update when mater data is re-processed)
business_days <- seq(date_start, date_end, by="days")[!is.weekend(seq(date_start, date_end, by="days"))]
missing_chg_cutOff <- business_days[length(business_days)-3] # Should this be 2 or 3?
```


```{r Open Encounters Metric Trending by Site, fig.width=12, fig.height = 5, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}
site_cols <- c("#212070","#d80b8c","#00aeef","#7f7f7f","#ffc000","#7030a0","#c7c6ef","#fcc9e9","#c9f0ff","#dddedd")
# Import in exclusion criteria
# Exclude ECHO encounters
missing_exc_dept <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_dept.xlsx")
missing_exc_resource <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_res.xlsx")
missing_exc_visitType <- read_excel("/nfs/data/Applications/Ambulatory/open_encounters_exclusion_visit.xlsx")
# missing_exc_dept <- read_excel("C:/Users/kweons01/Desktop/Strategic Initiatives - So Youn/Github/server-upload/open_encounters_exclusion_dept.xlsx")
# missing_exc_resource <- read_excel("C:/Users/kweons01/Desktop/Strategic Initiatives - So Youn/Github/server-upload/open_encounters_exclusion_res.xlsx")
# missing_exc_visitType <- read_excel("C:/Users/kweons01/Desktop/Strategic Initiatives - So Youn/Github/server-upload/open_encounters_exclusion_visit.xlsx")
# Based on Metric % Encounters Closed within 7 days
# Missing Charges Trending by Site
missing_chg_data_trend <- scheduling_data_raw %>%
  filter(Appt.Status == "Arrived") %>%
  filter(Resource == "Provider") %>%
  filter(Appt.DateYear >= date_start & Appt.DateYear <= missing_chg_cutOff) %>%
   mutate(clo.7days = case_when(open.days <= 7 ~ 'YES', TRUE ~ 'NO')) %>%
  # filter(Appt.DateYear >= as.Date("2021-06-01", "%Y-%m-%d")) %>%
  filter(Department %!in% unique(missing_exc_dept$DEPARTMENT)) %>%
  filter(Provider %!in% unique(missing_exc_resource$PROVIDER)) %>%
  mutate(visit_exclude = case_when(str_detect(Appt.Type, "ECHO|SOCIAL|NURSE|NUTRITION|LAB|TREATMENT") ~ "YES"
                                         ,TRUE ~ "NO")) %>%
  filter(visit_exclude == "NO") %>%
  # filter(enc.status == "CLOSED") %>%
  group_by(Campus, Appt.MonthYear, enc.status, clo.7days) %>%
  summarise(total = n()) %>%
   group_by(Campus, Appt.MonthYear) %>%
  mutate(total.enc = sum(total)) %>%
  pivot_wider(names_from = clo.7days,
              values_from = total,
              values_fill = 0) %>%
  mutate(clo.7days.perc = round((YES/(total.enc))*100,0)) %>%
  filter(enc.status == "CLOSED")

path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
saveRDS(missing_chg_data_trend, paste0(path,"missing_chg_data_trend.rds"))

```


```{r Open Encounters Metric Trending Summarized, fig.width=12, fig.height = 5, fig.align = 'center', echo = FALSE, warning = FALSE, message = FALSE}

missing_chg_data_trend_downtown <- scheduling_data %>%
   filter(Department %!in% unique(missing_exc_dept$DEPARTMENT)) %>%
  filter(Provider %!in% unique(missing_exc_resource$PROVIDER)) %>%
  filter(Appt.Status == "Arrived") %>%
  filter(Resource == "Provider") %>%
  mutate(visit_exclude = case_when(str_detect(Appt.Type, "ECHO|SOCIAL|NURSE|NUTRITION|LAB|TREATMENT") ~ "YES"
                                         ,TRUE ~ "NO")) %>%
  filter(visit_exclude == "NO") %>%
  filter(Campus %in% c("MSUS","MSDD","MSBI")) %>%
  mutate(Campus = "MS Downtown") %>%
  filter(Appt.DateYear >= date_start, Appt.DateYear <= missing_chg_cutOff) %>%
  # filter(Appt.DateYear <= missing_chg_cutOff) %>%
  # filter(enc.status == "CLOSED") %>%
  mutate(clo.7days = case_when(open.days <= 7 ~ 'YES', TRUE ~ 'NO')) %>%
  group_by(Campus, Appt.MonthYear, enc.status, clo.7days) %>%
  summarise(total = n()) %>%
   group_by(Campus, Appt.MonthYear) %>%
  mutate(total.enc = sum(total)) %>%
  pivot_wider(names_from = clo.7days,
              values_from = total,
              values_fill = 0) %>%
  mutate(clo.7days.perc = round((YES/(total.enc))*100,0)) %>%
  filter(enc.status == "CLOSED")

path <- "/nfs/data/Applications/Ambulatory/Data_Updated/"
saveRDS(missing_chg_data_trend_downtown, paste0(path,"missing_chg_data_trend_downtown.rds"))

```
